---
title: "corona - analysis"
author: "fadi abdelkabir"
date: "28/03/2020"
output:
  beamer_presentation: default
  html_document: default
  ioslides_presentation: default
  pdf_document: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#### importation ####

```{r}
url1<-'https://data.humdata.org/hxlproxy/api/data-preview.csv?url=https%3A%2F%2Fraw.githubusercontent.com%2FCSSEGISandData%2FCOVID-19%2Fmaster%2Fcsse_covid_19_data%2Fcsse_covid_19_time_series%2Ftime_series_covid19_confirmed_global.csv&filename=time_series_covid19_confirmed_global.csv'

confirmed_df<- read.csv(url1, header = TRUE, sep = ',',check.names=FALSE)

View(confirmed_df)

```



#### data preparation ####
##### partie 1 vectors #####

```{r}
tunisie = confirmed_df[confirmed_df$'Country/Region'=='Tunisia',]
tunisie=tunisie[,5:ncol(tunisie)]
tunisie=tunisie[,tunisie>0]
tunisia=colSums(tunisie)
tunisia=as.vector(tunisia)
View(tunisia)
tun_ts=ts(tunisia)
plot(tunisia)
plot(tun_ts)
```

##### partie 2 dates #####
```{r}
dates = colnames(tunisie[1:ncol(tunisie)])
```

#### modeling and predictions #### 
##### case understanding #####

```{r}
" * we we'll make a new dataframe called 'newtunisie' the first column will       take the exact numbers of the confirmed cases.
  * then we will start to build the predictive models based on the fist 15        observation.
  * the second column will be for zakaria's model with coef = 1.2.
  * the third column will use the forecast or predict function.
  * in the end we will compare the three results with a ggplot.
```

##### model 0.1  ' zakaria ' preparation ####

```{r}
length(tunisia)
added = tunisia[1:15]
added_es=tunisia
newtunisie= cbind(tunisia,added_es)
newtunisie=data.frame(newtunisie)
last= added[length(added)]
for (i in (length(added)+1):length(tunisia)){
  newtunisie$added_es[i]=round(last*1.2)
  last=newtunisie$added[i]
}
added
View(newtunisie)
```


##### model 0.2 ' new ' preparation ####

```{r}
require(forecast)

days= seq(0,(length(added))-1)
days=as.vector(days)
tun_ts1=ts(added,start = 0)
plot(tun_ts1)
pred<-forecast(tun_ts1)
pred
prediction=pred$upper[,2][0:9]
prediction
pre_added=round(c(added,prediction))
pre_added
length(pre_added)
newtunisie= cbind(newtunisie,pre_added)
newtunisie$tunisia=as.numeric(newtunisie$tunisia)
newtunisie$added_es=as.numeric(newtunisie$added_es)
newtunisie$pre_added=as.numeric(newtunisie$pre_added)
newtunisie=data.frame(newtunisie)
View(newtunisie)
```


#### visualization ####

```{r}
library(ggplot2) 
graph  = ggplot(data = newtunisie) + geom_line( aes(x = date, y = newtunisie$tunisia, colour = "confirmed cases ")) + geom_line( aes(x = date , y = newtunisie$added_es, colour = "estemated by 1.2"))+ geom_line( aes(x = date , y = newtunisie$pre_added, colour = "estemated by forcast fun"))
graph +ggtitle("COVID-19 CASES IN TUNISIA")+labs(x = "NUMBER OF DAYS",y = "NUMBER OF CASES") +  scale_colour_manual(values=c("blue", "red","yellow")) + theme(legend.position=c(0.1, 0.1), legend.justification = c("left","bottom")) 
```

##### interpretation ##### 
```{r}
" * as we can see from the graph that zakaria's is not correct and the            predicted values are so far from the real values same goes with the           forcast function '
```


#### TESTS ####

```{r}
print("t-test for zakaria's model")
t.test(newtunisie$added_es,newtunisie$tunisia) 

print("t-test for the forecast function model ")
t.test(newtunisie$pre_added,newtunisie$tunisia) 

```


#### interpretation ####

```{r}
" * so the p-values prouves our interpretation from the graph 
  * model 0.1 : p-value = 0.4277 < 0.05 we reject H0 and accept H1: theres a significant difference in the predicted values and the real values 

  * model 0.2 : p-value = 0.5725 < 0.05 we reject H0 and accept H1: theres a significant difference in the predicted values and the real values 
"
```




#### ARIMA ####

```{r}
library(forecast)
fit <- auto.arima(tun_ts)
fit
fcast <- forecast(fit)
fcast
```

#### interpretation ####

```{r}
" *  -0.4956 is significant
  * i'll be testing these results in a weeks time with the real cases to see how good is this prediction and can we rely on it automaticly in the futur
"
```


#### more analysis ####

```{r}
dayss=seq(0,length=length(dates))
tun_ts2=ts(tunisia,start = 0)
```


##### regression linéaire de la tendance #####


```{r}
temps = dayss
linearreg= lm(tun_ts2~dayss)
summary(linearreg)
fv=linearreg$fitted.values # les valeurs estimés
temp_fit_line=ts(fv,start = 0)
```


##### regression polynomial de la tendance ####


```{r}
tempsq = temps*temps
ploy_reg=lm(tun_ts2~temps+tempsq)
summary(ploy_reg)
fv1=ploy_reg$fitted.values
temp_fit_poly=ts(fv1,start = 0)
```


##### regression moving average  de la tendance ##### 


```{r}
library(stats)
length(tun_ts)
moving_avg=filter(tun_ts,method='convolution',sides=2,filter=array(1/4,dim = 4))
moving_avg
# plus la pas est elévée plus la representation est lisse
moving_avg_ts=ts(moving_avg,start=0)
```


##### local poly regression  #####

```{r}
loc_reg=loess(tun_ts2~dayss)
loc_reg.fit=ts(loc_reg$fitted,start=0)
```

##### representation #####

```{r}
library(ggplot2)
graph1  = ggplot(data = tun_ts2) + geom_line( aes(x = dayss, y = tun_ts2, colour = "confirmed cases ")) + geom_line( aes(x = dayss , y = loc_reg.fit, colour = "loc ploy reg")) + geom_line(aes(x=dayss,y=temp_fit_line,colour = "linear reg"))+ geom_line(aes(x=dayss,y=temp_fit_poly,colour = "poly reg")) + geom_line(aes(x=dayss,y=moving_avg_ts,colour = "moving average reg")) 
graph1
```

#### interpretation ####

```{r}
" * from this graph it look like the tendency of the dataset takes the shape of the tendency of localy polynomial regression ' they are very close in shape and values '
"
```


#### model shaping ####
##### case understanding #####

```{r}
" * for this model i choosed not put a saisonality for the reason that we lac information, it s a values for pandemic infection and it is very conditionaly so it doesnt have a frequent behavior so i ll just remove the tendency 
"
```

#### shaping ####

```{r}
new_tun=tun_ts2-(loc_reg.fit)
plot(new_tun)
```



```{r}
require(tseries)
kpss.test(new_tun)
```

```{r}
"  * p-value=0.1 is grater then 0.05 => means : we accept The null hypothesis for the test is that the data is stationary.
"
```


```{r}
shapiro.test(new_tun)
```
```{r}
"  * the p-value is less than 0.05, then the null hypothesis that the data are normally distributed is rejected. 
"
```


